Near instantaneous response of mesophyll conductance to light availability allows shade leaves to lie in wait

### 2015-07-31 manuscript/manuscript_wtc3.Rmd
fixed a space

\
First, g~s~ should be efficiently distributed within a canopy to utilize supplies of light, N and water to maximize A [@peltoniemi2012co]. This is because stomata are hypothesized to exhibit an optimal behaviour to maximize C gain while simultaneously minimizing water loss through transpiration [@cowan1977stomatal]. Second, variation in photosynthetic capacity between sun and shade leaves has also been hypothesized to be due to differences in g~m~ [@duursma2006vertical]. Mesophyll conductance can impose limitations on A as large as those associated with g~s~ [@warren2008stand; @ubierna2011estimation]and these limitations can reduce the efficiency of N use in A [@niinemets2007photosynthesis]. Interpreting the coupled responses of both g~s~ and g~m~ to A across sun and shade leaves has major implications for predicting canopy C gain, but empirical measurements across tree canopies are still lacking.

>>>>

\
First, g~s~ should be efficiently distributed within a canopy to utilize supplies of light, N and water to maximize A [@peltoniemi2012co]. This is because stomata are hypothesized to exhibit an optimal behaviour to maximize C gain while simultaneously minimizing water loss through transpiration [@cowan1977stomatal]. Second, variation in photosynthetic capacity between sun and shade leaves has also been hypothesized to be due to differences in g~m~ [@duursma2006vertical]. Mesophyll conductance can impose limitations on A as large as those associated with g~s~ [@warren2008stand; @ubierna2011estimation] and these limitations can reduce the efficiency of N use in A [@niinemets2007photosynthesis]. Interpreting the coupled responses of both g~s~ and g~m~ to A across sun and shade leaves has major implications for predicting canopy C gain, but empirical measurements across tree canopies are still lacking.
